### 2022-09-21 main/chapter_context.tex
add more citations for heavy standard model paragraph, begin notes for susy

Both \atlas\ and \cms\ have now found a Higgs boson candidate at
$m(H) = 125\,\eV[G]$~\cite{
atlas2012higgs,
atlas2012combined,
cms2012higgs
}
and confirmed all of its tested Standard Model properties~\cite{
combined2016higgs,
atlas2022ten,
cms2022ten
}
such as its production mechanisms, decay rates,
spin, and parity~\cite{HIGG-2013-01, HIGG-2013-17, HIGG-2014-06}.

@@

\TODO{standard model~\cite{atlas2021summarysm}}

\TODO{top mass~\cite{atlas2022symmarytop, atlas2019topmass}}

\TODO{Top factory. The top quark's almost-exclusive decay as $t\rightarrow Wb$ ... $b$ sensitivity}
% top physics: tttt, ttH
% rare ZZy ?
% W mass measurement

\TODO{$W$ mass~\cite{atlas2018wmass}}
\TODO{`diboson' $WZ$ $W\gamma$}

\TODO{B-physics (supplements dedicated results from \lhcb)}

\TODO{w mass conflict~\cite{cdf2022high}}

\paragraph{Discover new (supersymmetric) particles.}
This is not a failure. It is a success.
Our goal is not to discover something that is not there, but to learn more
about nature.
The nonappearance of supersymmetric particles at the LHC is itself a discovery.

@@

$\twoljets$ piggyback on the $ZZ \to \ell\ell\nu\nu$ channel

>>>>

Both \atlas\ and \cms\ have now found a Higgs boson candidate at
$m(H) = 125\,\eV[G]$~\cite{
atlas2012higgs,
atlas2012combined,
cms2012higgs
}
and confirmed all of its tested Standard Model properties~\cite{
combined2016higgs,
atlas2022ten,
cms2022ten
}
such as its production mechanisms, decay rates,
spin, and parity~\cite{
HIGG-2013-01,
HIGG-2013-17,
HIGG-2014-06
}.

@@

\atlas\ has now produced a plethora of competitively precise measurements
of the heavy Standard Model~\cite{atlas2021summarysm},
including $m(W)$~\cite{atlas2018wmass} and
$m(t)$~\cite{atlas2022symmarytop, atlas2019topmass, TOPQ-2015-03},
but also details of differential cross-sections~\cite{
STDM-2016-11,
STDM-2016-14,
TOPQ-2018-15,
TOPQ-2016-10
}.
Rare processes have also been studied in new levels of detail,
including
electroweak diboson ($WW/WZ/ZZ$ etc.)~\cite{
STDM-2015-21,
STDM-2015-23,
STDM-2017-09
}
and triboson~\cite{
STDM-2016-06,
STDM-2017-22,
STDM-2019-09
},
and rare top processes
($\ttbar Z$, $\ttbar W$ etc.)~\cite{
TOPQ-2013-05,
TOPQ-2018-01,
TOPQ-2020-03
},
These continue to not validate the Standard Model, and are aided by the lack of
new phenomena, which could have overpowered such rare signals.

\paragraph{Discover new (supersymmetric) particles.}
\TODO{
has discovery potential up to multi-TeV mass scales,
expect decays to knwon particles, so complements Higgs,
discovery and Standard Model measurements,
indeed search of this analysis benefits both from ZZ llvv and Hbb,
$\twoljets$ piggyback on the $ZZ \to \ell\ell\nu\nu$ channel
}

This is not a failure. It is a success.
Our goal is not to discover something that is not there, but to learn more
about nature.
The nonappearance of supersymmetric particles at the LHC is itself a discovery.

@@
